### 2016-12-12 paper/chapters/gan.tex
clarified some GAN stuff

@@

\subsection{Training}
\label{sub:gan_training}
The GAN framework can be fully trained with stochastic backpropagation due to both $D$ and $G$ being differentiable.

Combining the loss functions of both generator and discriminator yields us the following objective with value function $V(G,D)$.
$$
\min_G \max_D V(D,G) = \mathbb{E}_{x \sim p_{data}}[\log D(x)] + \mathbb{E}_{z \sim p_z(z)}[\log(1 - D(G(z)))]
$$
In the original GAN paper an minibatch-based algorithm for training GAN is proposed, but we will take a look at an the online learning version below:\\
\begin{algorithm}
  \caption{Online learning of generative adversarial networks $-$ simple version ($k=1$)}
  \label{alg:gan_online}
  \begin{algorithmic}[1]
    \Let{$\eta_d, \eta_g$}{Learning rate of discriminator and generator networks, respectively}
    \Let{$\theta_d, \theta_g$}{Parameters of function approximators}
    \For{number of training iterations}
      \Let{$z_d$}{sample from noise prior $p_g(z)$}
      \Let{$z_g$}{sample from noise prior $p_g(z)$}
      \Let{$x$}{example from training set}
      \Let{$\theta_d$}{$\theta_d + \eta_d \nabla_{\theta_d} \bigg[\log D(x) + \log \big(1 - D(G(z_d))\big)\bigg]$}
      \Let{$\theta_g$}{$\theta_g - \eta_g \nabla_{\theta_g} \bigg[\log\big(1 - D(G(z_d))\big)\bigg]$}
    \EndFor
  \end{algorithmic}
\end{algorithm}

In algorithm \ref{alg:gan_online} the original algorithm has been modified for single pass (online) learning.
Sampling minibatches from the noise prior and $p_{data}(x)$ result in the minibatch version.
Additionally, it is often required for practical reasons to let the discriminator run multiple backward passes while updating the generator once (why?).
Note that the discriminator will ascend while the generator descend its gradient due to maximizing $\mathcal{C}_d$ but minimizing $\mathcal{C}_g$ (correct?).

>>>>

% use of words: forgery
To understand the inuition behind the approach to GANs, it may be helpful to view(?) analogy of counterfeiters and the police.
Counterfeiters try to produce fake money imitating legit money while the police tries to distinguish fake from real money.
This procedure of generating and distinguishing will go back-and-forth as the counterfeiters will get better at producing authentic looking money and the police is hard-pressed to differentiate between fake and real.
Eventually, this procedure will result in a nash equlibrium where the police or discriminator will have 50\% chance of seperating authentic from real.

Ideally, we want to find this equilibrium for the GAN model as well.

@@

\subsection{Training}
\label{sub:gan_training}
Combining the loss functions of both generator and discriminator yields us the following objective with value function $V(G,D)$.
$$
\min_G \max_D V(D,G) = \mathbb{E}_{x \sim p_{data}}[\log D(x)] + \mathbb{E}_{z \sim p_z(z)}[\log(1 - D(G(z)))]
$$

The GAN framework can be fully trained with stochastic backpropagation due to $V(G,D)$ being differentiable.
Training will oscillate between training the generator and discriminator, where the other party is fixed respectively.
In order to avoid a too strong discriminator (or generator), the ratio of learning steps will vary even though there are no hard rules for this.

\paragraph{Theoretical Foundation}
Using a model with infinite training time and capacity in both generator and discriminator allows theoretical analysis of the GAN framework \cite{gan:2013}.
For any given generator $G$, the optimal discriminator $D$ is given by $D_G^*(x)$:
$$
D_G^*(x) = \frac{p_{data}(x)}{p_{data}(x) + p_{model}(x)}
$$

%In the original GAN paper an minibatch-based algorithm for training GAN is proposed, but we will take a look at an the online learning version below:\\
%\begin{algorithm}
  %\caption{Online learning of generative adversarial networks $-$ simple version ($k=1$)}
  %\label{alg:gan_online}
  %\begin{algorithmic}[1]
    %\Let{$\eta_d, \eta_g$}{Learning rate of discriminator and generator networks, respectively}
    %\Let{$\theta_d, \theta_g$}{Parameters of function approximators}
    %\For{number of training iterations}
      %\Let{$z_d$}{sample from noise prior $p_g(z)$}
      %\Let{$z_g$}{sample from noise prior $p_g(z)$}
      %\Let{$x$}{example from training set}
      %\Let{$\theta_d$}{$\theta_d + \eta_d \nabla_{\theta_d} \bigg[\log D(x) + \log \big(1 - D(G(z_d))\big)\bigg]$}
      %\Let{$\theta_g$}{$\theta_g - \eta_g \nabla_{\theta_g} \bigg[\log\big(1 - D(G(z_d))\big)\bigg]$}
    %\EndFor
  %\end{algorithmic}
%\end{algorithm}

%In algorithm \ref{alg:gan_online} the original algorithm has been modified for single pass (online) learning.
%Sampling minibatches from the noise prior and $p_{data}(x)$ result in the minibatch version.
%Additionally, it is often required for practical reasons to let the discriminator run multiple backward passes while updating the generator once (why?).
%Note that the discriminator will ascend while the generator descend its gradient due to maximizing $\mathcal{L}_d$ but minimizing $\mathcal{L}_g$ (correct?).
